Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-16 forecast/paper/paper.tex
Revise dated and add figs marked TODO to manuscript.

\begin{figure}[tb!]
\includegraphics[width=\columnwidth]{fig/vintage.pdf}
\caption{TODO}
\label{fig:vintage}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{fig/trajectory.pdf}
\caption{TODO}
\label{fig:trajectory}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{fig/fcast-1.pdf}
\caption{TODO}
\label{fig:forecast}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{fig/hot-1.pdf}
\caption{TODO}
\label{fig:hotspot}
\end{figure}

@@

TODO

@@

TODO

>>>>

\begin{figure}[tb!]
\includegraphics[width=\columnwidth]{fig/revisions-dv-jhu-1.pdf}
\caption{Revision behavior for signals in the New York City HRR from two
  sources. Each colored line 
  corresponds to the data as reported on that date. DV-CLI is revised upward
  throughout the month of December, though the amount fades as we look further
  back in time. In contrast, JHU-CSSE data remains ``as reported'' on
  December 3 until a major correction is made on December 31, affecting all data
  over the period. }
\label{fig:vintage}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{fig/ny-trajectory-1.pdf}
\caption{Forecast from the autoregressive model for the New York City HRR made
  on October 15 (vertical line). 
  The fan displays 50\%, 80\% and 95\% intervals while the orange curve shows
  the median forecast. The connected black points represent ``finalized'' data,
  as reported in May 2021.}
\label{fig:trajectory}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/fcast-1.pdf}
  \caption{Average WIS for each forecast model divided by the averaged WIS of
    the flat-line forecaster.}
  \label{fig:forecast}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{fig/hot-1.pdf}
\caption{Area under the curve for each forecast model averaged over all
  prediction dates and HRRS.}
\label{fig:hotspot}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/upswing-histogram-1.pdf}
  \caption{Histogram of the difference in WIS for the AR model relative to each
    forecaster. Larger values are better for the indicator assisted model.}
  \label{fig:up-down-flat}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/leading-and-lagging-1.pdf}
  \caption{Correlation of the difference in WIS with the ``leadingness'' and
    ``laggingness'' of the indicator at the target date.}
  \label{fig:leading-lagging}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/diff-in-lead-lag-1.pdf}
  \caption{Correlation of the difference in WIS with difference between the
    ``leadingness'' and ``laggingness'' of the indicator at the target date.}
  \label{fig:diff-btw-leading-lagging}
\end{figure}
